Experiences with Planning for Natural Language Generation

### 2008-06-23 trunk/Papers/experiences/domains.tex
small changes

Plan execution monitoring also plays an important role in the GIVE problem.
At a high level, the system needs to monitor a user's actions and compare
them against the generated instruction set to determine if the user has
correctly followed directions or not. In the case of the latter, new
instructions may have to be generated. In practice, the situation
can be quite complicated since the mental state of the user is not known
and so the system must observe the user's actions in real time. For
example, a user directed to ``turn around and walk through the door'' may
not necessarily perform these actions to the letter, i.e., immediately
turning 180 degrees and proceeding directly to the door. Instead, the user
might take a roundabout route through the room, eventually exiting out the
door. Although the user's actions do not match the generated instructions
exactly, they meet the intended goal. The system must be able to identify
such ``equivalent'' plans and not immediately generate new instructions as
soon as the user's actions have gone off course. Furthermore, a user can
communicate certain intentions to the system, both through action and
inaction. For instance, the system may correctly infer that a user has
failed to follow instructions if the user exits a room when given a
directive to ``walk to the centre of the room''. However, the system should
also be able to make a similar conclusion if a user simply does nothing
when given the instruction. Thus, such real-time plan monitoring is
essential in the GIVE domain, and also affects other modules in the system.

>>>>

Plan execution monitoring also plays an important role in the GIVE problem.
At a high level, the system needs to monitor a user's actions and compare
them against the generated instruction set to determine if the user has
correctly followed directions or not. In the case of the latter, new
instructions may have to be generated. In practice, the situation
can be quite complicated since the mental state of the user is not known
and so the system must observe the user's actions in real time. For
example, a user directed to ``turn around and walk through the door'' may
not necessarily perform these actions to the letter, i.e., immediately
turning 180 degrees and proceeding directly to the door. Instead, the user
might take a roundabout route through the room, eventually exiting out the
door. Although the user's actions do not match the generated instructions
exactly, they meet the intended goal. The system must be able to identify
such ``equivalent'' plans and not immediately generate new instructions as
soon as the user's actions have gone off course. Furthermore, a user can
communicate certain intentions to the system, both through action and
inaction. For instance, the system should infer that a user has failed to
follow instructions if the user exits a room when given a directive to
``walk to the centre of the room''. However, the system should also make a
similar conclusion if a user simply does nothing when given the
instruction. Such real-time plan execution monitoring is essential in this
domain.

%However, the system should also be able to make a similar conclusion if a
%user simply does nothing when given the instruction. Thus, such real-time
%plan monitoring is essential in the GIVE domain, and also affects other
%modules in the system.
